### 2018-05-09 4_impl.tex
place the interpreter picture.

This section describes program units that construct, transform and analyse internal representations described before. % steps of construction of the program representations and transformations applied to them.
Further in this Section, the subsection titles have a number in parentheses, which correspond to a unique number of the  processing unit being discussed.
This numbers are pictured within gears on the top-left corner of each processing unit in Figure~\ref{fig:arch}.
%he numbers in parentheses correspond the numbers of processing units pictured within gears in Figure~\ref{fig:arch}.

@@

\begin{figure}[th]
    \centering
  %draft=true
  \includegraphics[max width=\textwidth,keepaspectratio]{img/my/draw.io/X-compiler.png}
  \caption{Main components of the X-compilation processing unit}
  \label{fig:compiler}
\end{figure}

The X-graph compiler is the main component that transforms the recursive \ytree{} data structure to the plain \xgraph{} representation.

The compilation is performed in three stages.
Firstly, the \ytree{} is compiled to a \textit{cyclic} control-flow event-based graph \xgraph[CF].
Then, this graph is unrolled to an \textit{acyclic} control-flow event-based graph \xgraphU[CF].
After that, the compiler is able to perform the data-flow analysis and produce the full event-based graph \xgraphU[CF+DF], which remains to be CF-acyclic (no cycles among control-flow edges).

The X-compiler is a complex processing unit, Figure~\ref{fig:compiler} illustrates the relationship the principal components of the X-compiler in the UML language.

>>>>

This section describes program units that construct, transform and analyse internal representations described before. % steps of construction of the program representations and transformations applied to them.
Further in this Section, the subsection titles have a number in parentheses, which correspond to a unique number of the  processing unit being discussed.
These numbers are pictured within the gear in the top-left corner of each processing unit in Figure~\ref{fig:arch}.
%he numbers in parentheses correspond the numbers of processing units pictured within gears in Figure~\ref{fig:arch}.

the full \xgraph{} construction is performed in three stages.
First, the \ytree{} is compiled to a \textit{cyclic} control-flow event-based graph \xgraph[CF].
Then, this graph is unrolled to an \textit{acyclic} control-flow event-based graph \xgraphU[CF].
After that, the compiler is able to perform the data-flow analysis and produce the full event-based graph \xgraphU[CF+DF], which remains to be \textit{CF-acyclic} (no cycles among control-flow edges).

@@

The X-compiler is the main component that transforms the recursive \ytree{} data structure to the plain \xgraph{} representation.

\begin{figure}[!t]%[H]
    \centering
  %draft=true
  \includegraphics[max width=\textwidth,keepaspectratio]{img/my/draw.io/X-compiler.png}
  \caption{Main components of the X-compilation processing unit}
  \label{fig:compiler}
\end{figure}

The It is a complex processing unit, Figure~\ref{fig:compiler} illustrates the relationship between the principal components of the X-compiler in the UML language.
